%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
I started a Ph.D. because when I finished my degree I felt that I had learned very few things about Engineering. It is funny that now that I  finished the thesis, I feel kind of the same way. Even worse, the more I study, the more I understand that I have many lessons to learn. I realised that there are two kinds of  people, those who don't know and those who don't know they don't know. Those who study all their life and those who think they know everything. When you are a scientist, you surely are  one of the students. 

I am a privileged person, I am very lucky. I was granted with the opportunity to put a brick in the wall of science. I stood on the shoulders of giants as many people did before me.  It is even more exciting to participate in the growing of robotics, a very young science in comparison with others like physics or mathematics. In the next decades there will be robots collaborating with us and this future will have a piece of my work and effort. 

I would like to express my deepest gratitude to everyone that have accompanied me in all this years of learning. Therefore, I would like to propose a toast:

To Carlos Balaguer. For his leadership and kindness. For giving me the opportunity to learn at his side. For all the time he has given me, which is more valuable knowing he does not have much. And for his guidance and help in all the  decisions I have made. 

To Thrishantha Nanayakkara. For accepting me as his Ph.D student and giving me the opportunity of being part of his research group in London. For everything that I have learned from him and all the things I  will learn. For his wisdom and knowledge. And for being so close even though we were so far. 

To Luis Moreno and Santiago Garrido. For being my  Ph.D. advisors in the shadows. For all that have learned from them and for answering all my questions. 

To Juan Gonz{\'a}lez V{\'i}ctores, Daniel Hern{\'a}ndez, Martin Stoelen and V{\'i}ctor Gonz{\'a}lez Pacheco. For all the ideas and experiences we have shared.

To Jorge Garc{\'i}a Bueno and Alejandro Mart{\'i}n. For being my partners in the difficult adventure of creating a company.

To  Concha Monje, Dolores Blanco, Paolo Pierro, Alberto Jard{\'o}n, Javier Gorostiza, Ram{\'on} Barber and Santiago Mart{\'i}nez de la Casa. For  helping me every time I have needed them and for all the funny moments we have lived together. 

To Raúl Perula, Juanmi García Haro, Santi Morante, Javier Quijano and  every member of RoboticsLab. For all the jokes and the good experiences.

To Sonia Mata and Eduardo Silles. For solving many problems and being always ready to help.

To Juan Dom\'inguez. For being the one to encourage me to study Industrial Engineer.

To David L{\'o}pez del Moral, Mª Jes{\'u}s G{\'o}mez and Eduardo Corral. For being as crazy as I am to do a Ph.D. and for all the afternoons we have spent together.

To Miguel Maldonado. For being my brother. For supporting me, working with me and helping me. And for being at my side so many time.

To my father, sister, grandparents and the rest of my family. For their support and love.

To my mother. For being the best mother anyone can desire. For his wisdom and dedication.

To my wife. For being everything to me.

\vspace{20mm}
\begin{flushright}
\textit{Gracias a todos}
\end{flushright}
\begin{flushright}
\textit{Miguel}
\end{flushright}





